A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-11-26 paper/paper.tex
paper: minor polish

\subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
The construction relies on the groupoid properties of equality in some places, which have to be made explicit in the formalization.

Notice that in table~\ref{fulltab:coh}, the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd). (u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type is left implicit. Also implicit is the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, or functional extensionality, holds by default in extensional type theory.

@@

By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~(\citeyear{altenkirch15}), we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models. In particular, we wonder whether the indexed approach might provide definitional properties which are otherwise lost when detouring via presheaves. In particular, we conjecture being able to justify univalence holding definitionally. Our approach would also definitively ground cubical type theory in iterated parametricity.

>>>>

\subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
The construction relies on the groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}. The use of the equivalence between $u = v$ and $\Sigma (p:u.\hd = v.\hd). (u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type is left implicit in the same table. Also implicit is the use of the equivalence between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, or functional extensionality, holds by default in extensional type theory. These have to be made explicit in the formalization.

@@

By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models. In particular, we wonder whether the indexed approach might provide definitional properties which are otherwise lost when detouring via presheaves. In particular, we conjecture being able to justify univalence holding definitionally. Our approach would also definitively ground cubical type theory in iterated parametricity.
